\chapter{Library}

\section{Types}

\noindent An implementation shall provide handling for the following types:

\bullet{\tt FPAP\_BYTE} The type representing a single byte.
\bullet{\tt FPAP\_WORD} The type representing two bytes.
\bullet{\tt FPAP\_DWORD} The type representing four bytes.
\bullet{\tt FPAP\_COORD} The type representing a pixel coordinate.
\bullet{\tt FPAP\_COLOR} The type representing a color.
\bullet{\tt FPAP\_BOOL} The type representing a boolean.
\bullet{\tt FPAP\_PROPERTY} The type representing a propery of an instance.
\bullet{\tt FPAP\_ERROR} The type representing an error code.
\bullet{\tt FPAP\_PTR} The type representing an address.
\bullet{\tt FPAP\_STR} The type representing a pointer.
\bullet{\tt FPAP} The type representing a pointer to the current instance.

\section{Functions}

\noindent The following functions shall exist:

\definitions
\name{fpap\_init}
\code
FPAP\_ERROR fpap\_init(FPAP instance, FPAP\_COORD width, FPAP\_COORD height,\cr
\qquad FPAP\_STR name)\cr
\ecode
\noindent The implementation shall create a new instance, initialise the
window system and create a new window. The region of the window shall be
determined in an implementation defined manner using the width and height
arguments. The name is used in an implementation defined manner to register
the window with the window system.

\leftline{\tt ERRORS}
\error FPAP\_SUCCESS: No error.
\error FPAP\_NO\_WINDOW\_SYSTEM: Could not initialise window system.
\error FPAP\_NO\_WINDOW: Could not not initialise window.
\next{fpap\_term}
\code
FPAP\_ERROR fpap\_term(FPAP instance)\cr
\ecode
\noindent The implementation destroy the instance, window system, and window
in an implementation defined way. Further reference to the instance specified
is undefined behaviour.

\leftline{\tt ERRORS}
\error FPAP\_SUCCESS: No error.
\next{fpap\_frame}
\code
FPAP\_ERROR fpap\_frame(FPAP instance)\cr
\ecode
\noindent The window system shall write any unwritten pixels from the
framebuffer to the window and return any required information to the instance.

\leftline{\tt ERRORS}
\error FPAP\_SUCCESS: No error.
\error FPAP\_WINDOW\_CLOSED: The window has been closed, it is undefined
behaviour to re-call \tt fpap\_frame \rm after this point.
\next{fpap\_draw}
\code
FPAP\_ERROR fpap\_draw(FPAP instance, FPAP\_COLOR *content,\cr
\qquad FPAP\_COORD width, FPAP\_COORD height)\cr
\ecode
\noindent Content shall be written to the framebuffer, scaled such that the
written content convers the entirety of the framebuffer and no more. The
width and height designate the geometry of content.

\leftline{\tt ERRORS}
\error FPAP\_SUCCESS: No error.
\next{fpap\_set}
\code
FPAP\_ERROR fpap\_set(FPAP instance, FPAP\_PROPERTY, FPAP\_PTR value)\cr
\ecode
\noindent The implementation defined property specified shall be set to the
region of memory at that specified in value.

\leftline{\tt ERRORS}
\error FPAP\_SUCCESS: No error.
\error FPAP\_UNDEFINED\_PROPERTY: Property specified does not exist.
\error FPAP\_INACCESSIBLE: Property could not currently be specified.
\next{fpap\_get}
\code
FPAP\_ERROR fpap\_get(FPAP instance, FPAP\_PROPERTY, FPAP\_PTR value)\cr
\ecode
\noindent The region of memory specified in value shall be set to the
implementation defined property specified.

\leftline{\tt ERRORS}
\error FPAP\_SUCCESS: No error.
\error FPAP\_UNDEFINED\_PROPERTY: Property specified does not exist.
\error FPAP\_INACCESSIBLE: Property could not currently be specified.
\edefinitions

\vfill\break
